Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-01-04 doc_v2/doc_v2.Rmd
rephrasing sentences

Figure \ref{fig:type1} compares nominal (fixed) type I error and actually observed type I errors for the parameter settings in table \ref{tab:param}. With an increasing size of the window used in the optimization step the observed type I error rate decreases (slighty)or As the optimization window increase the observed type I error rate gets smaller, while, A smaller validation window tends to be associated with a higher type I error rate. This can be better imagined for a given window of optimization, when the actual Type I error is comparable to the nominal level for only a select few validation window sizes and for comparable validation window sizes of 30 and 50 as done here, the actual type I error although increases negligibly, it does not seem to vary as much as it varies with the optimization window sizes. This might be related to the increasing number of tests that fail for larger window sizes, in particular for non-matching striae (see fig \ref{fig:missings}).

>>>>

Figure \ref{fig:type1} compares nominal (fixed) type I error and actually observed type I errors for the parameter settings in table \ref{tab:param}. With an increasing size of the window used in the optimization step the observed type I error rate decreases (slighty). This means as the optimization window increase the observed type I error rate gets smaller. A smaller validation window on the other hand, tends to be associated with a higher type I error rate. This can be better imagined for a given window of optimization, where the actual Type I error is comparable to the nominal level for only a select few validation window sizes. For these comparable validation window sizes of 30 and 50 as done here, the actual type I error increases very slightly and can be seen in Figure \ref{fig:type1}. This increase is not as much when compared to the variation seen with the optimization window sizes. This effect might be related to the increasing number of tests that fail for larger optimization window sizes, in particular for non-matching striae (see fig \ref{fig:missings}).
